Canopy leaf area of a mature evergreen *Eucalyptus* woodland does not respond to elevated atmospheric [CO~2~] but tracks water availability

### 2015-05-21 manuscript.Rmd
Some changes to account for GCB format requirements. Sent around to co-authors as version 3.

@@

```{r echo=FALSE, message=FALSE}
source("manuscript_calcs.R")
```

@@

# Acknowledgments {.unnumbered}
We thank Steven Wohl, Vinod Kumar, Craig Barton and Craig McNamara for maintaining the FACE site and its wide array of sensors, and Andrew Gherlenda, Cassie Mosdal, Tamara Leetham and Catherine Beattie for significant efforts in separating and weighing the litter samples. We also thank Gerry Devine for support in data management. EucFACE is an initiative supported by the Australian Government through the Department of Industry and Science in partnership with the University of Western Sydney. Facilities and instrumentation at EucFACE were assembled as an initiative of the Australian Government as part of the Nation-building Economic Stimulus Package. Additional support from the Australian Research Council is acknowledged.

@@

```{r fig.width=8, fig.height=6, echo=FALSE, message=FALSE}
figure1(subset(facegap_cloudy_byring,Date < maxdate), ramp)
```

@@

```{r fig.width=4, fig.height=4, echo=FALSE, message=FALSE}
figure2(ba)
```

@@

```{r fig.width=8, fig.height=4, echo=FALSE, message=FALSE}
figure3(subset(facegap_cloudy_byring, Date < maxdate))
```

@@

```{r fig.width=6, fig.height=4, echo=FALSE, message=FALSE, echo=FALSE, message=FALSE}
figure4(dLAIlitter)
```

@@

```{r fig.width=8, fig.height=4, echo=FALSE, message=FALSE}
figure5(dLAIlitter)
```

@@

```{r fig.width=8, fig.height=4, echo=FALSE, message=FALSE}
figure6(ba)
```

@@

```{r fig.width=10, fig.height=8, echo=FALSE, message=FALSE}
figure7(subset(facegap_cloudy_byring, Date < maxdate),
               subset(facesoilwater, Date < maxdate),
               subset(faceraindaily, Date < maxdate),
               subset(airt, Date < maxdate))
```

@@

```{r fig.width=5, fig.height=8, echo=FALSE, message=FALSE}
figureSI1(litring, subset(facegap_cloudy_byring, Date < maxdate))
```

@@

```{r fig.width=8, fig.height=4, echo=FALSE, message=FALSE}
figureSI2(flatcan_byring)
```

@@

```{r fig.width=8, fig.height=5, echo=FALSE, message=FALSE}
figureSI3(subset(facegap_cloudy_byring, Date < maxdate), 
          subset(facegap_all_byring, Date < maxdate))
```

>>>>

\
*Running head* : Leaf area index in elevated [CO~2~]

@@

\
*Corresponding author*: 
Remko Duursma
E: remkoduursma@gmail.com
T: +61(0)422096908

\
*Type of Paper*:
Primary Research Article

```{r echo=FALSE, message=FALSE}
source("manuscript_calcs.R")

includeFigs <- FALSE
```

@@

# Acknowledgements {.unnumbered}
We thank Steven Wohl, Vinod Kumar, Craig Barton and Craig McNamara for maintaining the FACE site and its wide array of sensors, and Andrew Gherlenda, Cassie Mosdal, Tamara Leetham and Catherine Beattie for significant efforts in separating and weighing the litter samples. We also thank Gerry Devine for support in data management. EucFACE is an initiative supported by the Australian Government through the Department of Industry and Science in partnership with the University of Western Sydney. Facilities and instrumentation at EucFACE were assembled as an initiative of the Australian Government as part of the Nation-building Economic Stimulus Package. Additional support from the Australian Research Council is acknowledged.

@@

```{r fig.width=8, fig.height=6, echo=FALSE, message=FALSE, eval=includeFigs}
figure1(subset(facegap_cloudy_byring,Date < maxdate), ramp)
```

@@

```{r fig.width=4, fig.height=4, echo=FALSE, message=FALSE, eval=includeFigs}
figure2(ba)
```

@@

```{r fig.width=8, fig.height=4, echo=FALSE, message=FALSE, eval=includeFigs}
figure3(subset(facegap_cloudy_byring, Date < maxdate))
```

@@

```{r fig.width=6, fig.height=4, echo=FALSE, message=FALSE, echo=FALSE, message=FALSE, eval=includeFigs}
figure4(dLAIlitter)
```

@@

```{r fig.width=8, fig.height=4, echo=FALSE, message=FALSE, eval=includeFigs}
figure5(dLAIlitter)
```

@@

```{r fig.width=8, fig.height=4, echo=FALSE, message=FALSE, eval=includeFigs}
figure6(ba)
```

@@

```{r fig.width=10, fig.height=8, echo=FALSE, message=FALSE, eval=includeFigs}
figure7(subset(facegap_cloudy_byring, Date < maxdate),
               subset(facesoilwater, Date < maxdate),
               subset(faceraindaily, Date < maxdate),
               subset(airt, Date < maxdate))
```

@@

```{r fig.width=5, fig.height=8, echo=FALSE, message=FALSE, eval=includeFigs}
figureSI1(litring, subset(facegap_cloudy_byring, Date < maxdate))
```

@@

```{r fig.width=8, fig.height=4, echo=FALSE, message=FALSE, eval=includeFigs}
figureSI2(flatcan_byring)
```

@@

```{r fig.width=8, fig.height=5, echo=FALSE, message=FALSE, eval=includeFigs}
figureSI3(subset(facegap_cloudy_byring, Date < maxdate), 
          subset(facegap_all_byring, Date < maxdate))
```
